---
title: "Target Markdown"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(targets)
library(czso)
```

Target Markdown is a powerful R Markdown interface for reproducible analysis pipelines, and the chapter at https://books.ropensci.org/targets/markdown.html walks through it in detail. This R Markdown report the example from the chapter. Try it out in both interactive and non-interactive modes, either by running the code chunks in different ways or setting the `tar_interactive` chunk option.

# Packages

The example requires several R packages, and `targets` must be version 0.5.0.9000 or above. 

```{r, eval = FALSE}
install.packages(c("dplyr", "ggplot2", "readr", "targets", "tidyr", "czso", "visNetwork"))
```

# Setup

If you are using old versions of `targets` (<= 0.7.0) and/or `knitr` (<= 1.33), you will need to load the `targets` package in the R Markdown document in order for Target Markdown code chunks to work.

Near the top of the document, you may also wish to remove the `_targets_r` directory previously written by non-interactive runs of the report. Otherwise, your pipeline may contain superfluous targets.

```{r clean}
library(targets)
tar_unscript()
```

# Globals

We first define some global options/functions common to all targets. The function below plots a histogram of ozone concentrations, and our histogram target will need it.93.

```{targets globals, tar_globals = TRUE}
options(tidyverse.quiet = TRUE)
tar_option_set(packages = c("dplyr", "readr", "tidyr", "czso"))
```

# Targets

Our first target borrows the `airquality` dataset built into base R.

```{targets frozen}
czso:::czso_target_table(czs_frozen, "130185", dest_dir = "czs_frozen", freeze = TRUE)
```


```{targets live}
czso:::czso_target_table(czs_live, "130185", dest_dir = "czs_live", freeze = FALSE)
```

Set the `tar_simple` chunk option to `TRUE` to define a single target with the command in the code chunk. The chunk below only contains `biglm(Ozone ~ Wind + Temp, data)` in the source, but because `tar_simple` is `TRUE`, it is shorthand for `tar_target(name = fit, command = biglm(Ozone ~ Wind + Temp, data))`. All other arguments to `tar_target()` are set to their default values (configurable with `tar_option_set()`).

```{targets sum_dead_live, tar_simple = TRUE}
sum(czs_live_data$hodnota, na.rm = TRUE)
```

```{targets sum_dead_frozen, tar_simple = TRUE}
sum(czs_frozen_data$hodnota, na.rm = TRUE)
```


# Pipeline

If you ran all the `{targets}` chunks in non-interactive mode, then your R scripts are set up to run the pipeline.

```{r make}
tar_make()
```

# Output

You can retrieve results from the `_targets/` data store using `tar_read()` or `tar_load()`.

```{r readurl, message = FALSE}
tar_read(czs_live_url)
```


```{r readurl-frozen, message = FALSE}
tar_read(czs_frozen_url)
```

```{r readfile, message = FALSE}
tar_load(czs_live_file)

czs_live_file
file.size(czs_live_file)
```

```{r}
targets::tar_read(sum_dead_frozen)
targets::tar_read(sum_dead_live)
```


```{r readfile-frozen, message = FALSE}
tar_load(czs_frozen_file)

czs_frozen_file
file.size(czs_frozen_file)
```

```{r read-data-frozen}
targets::tar_read(czs_frozen_data)
```

```{r read-data-live}
targets::tar_read(czs_live_data)
```


The `targets` dependency graph helps your readers understand the steps of your pipeline at a high level.

```{r vis}
tar_visnetwork()
```

At this point, you can go back and run `{targets}` chunks in interactive mode without interfering with the code or data of the non-interactive pipeline.
